Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-21 paper/main.tex
consistencies and control contrasts

\begin{itemize}
    \item make more concise if applicable
\end{itemize}

@@

\begin{itemize}
    \item kürzen (war nicht ganz einfach)
    \item control contrasts ausformulieren
    \item adapt captions of result tables to new phrasing in intro / method
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
\end{itemize}

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occurring in spoken language.\todo{phrasing to delineate from Huth
(2016); imo voxel-wise semantic modeling says nothing about
excitation/inhibition}
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

@@

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually revealed by contrasting blocks of pictures can also be revealed by
contrasting selected stimulus features that incidentally occur under more
ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'' (AV stimulus).
% AO stimulus
The operationalization of auditory perception is based on an annotation of
speech occurring in the movie's audio-description (AD stimulus).
% GLM contrasts
Based on these annotations, we created several general linear model (GLM)
contrast to analyze the corresponding publicly available fMRI datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) of each naturalistic
stimulus \citep{hanke2016simultaneous, hanke2014audiomovie}.
% varying amount of data
Contrasts vary in HOW WELL / HOW MUCH DATA.\todo{rewrite if it should be
mentioned}

@@

% similar to previous studies
On the first level, we created GLM contrasts like studies that contrasted blocks
of pictures.
% dissimilar
But unlike previous studies, our approach was to contrast selected stimulus
features that we annotated in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).
% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
(2010) Notably, localization of the PPA in individual subjects that was done by
\citep{sengupta2016extension} using the established approach of contrasting
blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
\citep{sengupta2016extension}).\todo{maybe add note regarding Berman (2010); but
they did FFA}
% thus: primary contrasts
Here, we chose one contrast to be ``primary contrast'' for later detailed
inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /

@@

\todo[inline]{~1300 words (some sections incomplete)}

@@

\todo[inline]{SE: overlap of clusters/contrasts: Anzahl der Überlappungen ist
schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen; COH:
yes, I know it is kinda difficult, tried my best to choose/tweak the color map}

@@

% study goal
The goal of this study was to investigate if annotated cues about the spatial
layout embedded in two naturalistic stimuli correlate with increased hemodynamic
activity in the PPA that was defined using a visual localizer experiment within
the same subjects \citep{sengupta2016extension}.
% group level
On a group average level, we compare results gained from whole-brain GLM
analyses  of the movie and the audio-description (Z>3.4; p<.05, cluster
corrected) to results gained from the visual localizer.
% individual level
On the level single subjects (Z>3.4; p<.05, cluster corrected), we also assess
the performance of the exclusively auditory naturalistic stimulus as a
substitute for a visual paradigm to localize the PPA.\todo{``localize''}
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template can
found at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
\todo{still private collection}

% all AD contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r)
% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
% 4 PPA (l/r); RSC (l/r), LOC (l/r)
% 5 PPA (l/r); RSC (l/r), LOC (-/-)
% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C
% 8 PPA (-/-); RSC (-/-), LOC (-/-)
% ---------- control contrasts ----------
% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
%10 PPA (-/-); RSC (-/-), LOC (-/-)
%11 PPA (-/-); RSC (-/-), LOC (-/-),
%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
%13 PPA (-/-); RSC (-/-), LOC (-/-) results: PPA

% all AV contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
% intracalcarine, cuneal, ling.c
% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.
% ---------- control contrasts ----------
% 6 nothing
% 7 nothing
% 8 nothing
% 9 nothing
%10 se_new > se_old (nouns but in AV stimulus):
% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)

@@

\begin{table*}[h!]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting that was not depicted before to a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r. cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 6.56E-07 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 7.69E-06 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

% table group results primary AD contrast
\begin{table*}[h!]
    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
    \label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
188 & 5.96E-08 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
164 & 2.38E-07 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
\bottomrule
\end{tabular}
\end{table*}

@@

@@

% AV
Reliably across the five contrasts of the AV stimulus, we also find bilaterally
significant clusters also in the precuneal cortex (contrasts 1, 3, 4; all
bilateral)\todo{and? -> fsleyes} and lateral occipital cortex (all contrasts
except contrast 3)
% AD; LOC: AV cluster are more medial, AD clusters are more lateral
Reliably across the five contrasts of the AD, we find bilaterally significant
clusters in the ventral precuneus (7 contrasts), lateral occipital cortex
(bilateral in 4 contrasts, unilateral in 2 contrasts), superior temporal
cortices (4 contrasts)\todo{uni/bilateral?}.
%
\todo[inline]{(smallish) prefrontal clusters: 3 contrasts (non-overlapping)}

@@

% AV stimulus
AV stimulus. All contrasts using ``no cut condition'' > XY yield null results.
The contrast that uses the narrator's nouns but in the AV stimulus (se\_new >
se\_old): right PPA, bilateral sup. lat. occ. cortex; LOC (l/r), right superior
parietal lobe. Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new
setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
second highest correlation of a verbal cue category with a cut category; AND:
nouns that cue change to a familiar setting are somewhat correlated with cuts to
a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
category with a cut category).

% AD stimulus
AD stimulus (using annotation of movie cuts) all null results except: contrast 9
(vse\_new > pe\_old): right RSC.
% correlation of these nouns with cuts
Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new setting are
correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second highest
correlation of a verbal cue category with a cut category.

@@

\todo[inline]{~2100 words (some sections incomplete)}

@@

>>>>

\begin{itemize}
    \item make more concise if applicable
    \item add counts of intro, results, discussion respectively
\end{itemize}

@@

\begin{itemize}
    \item kürzen (war nicht ganz einfach)
    \item adapt captions of result tables to new phrasing in intro / method
    \item Simons Kommentare, bei denen ich mitunter anderer Meinung bin
    \item ggf. berichten welcher VIS Kontraste jeweils genommen wurde
\end{itemize}

@@

% Aziz (2008): place related sentences
To our knowledge only one study \citep{aziz2008modulation} investigated how
hemodynamic activity in the PPA differs between different semantic stimulus
categories occurring in spoken language.\todo{phrasing to delineate from Huth
(2016)}
% Aziz' stimuli
\cite{aziz2008modulation} used sentences that described generic or famous places
(e.g. ``The Taj Mahal faces a long thin reflecting pool''), faces (``Marilyn
Monroe has a large square jaw''), or objects (``The television has a long
antenna'').
% Aziz' tasks
Participants were instructed to press a button whenever the sentence described
an inaccurate or improbable fact.
% Aziz' results
Activation in the left, but not right, PPA was significantly reduced when
participants listened to place-related sentences compared to listening to
face-related sentences. Moreover, this effect was only observed in sentences
involving famous places.

@@

% open question
In this study, we investigate if increased hemodynamic activity in the PPA that
is usually revealed by contrasting blocks of pictures can also be revealed by
contrasting selected stimulus features that incidentally occur under more
ecologically conditions.
% we use 2 naturalistic stimuli
To answer this question, we operationalized the perception of both visual and
auditory spatial information using two naturalistic stimuli (see
\citep{hamilton2018revolution, hasson2008neurocinematics,
sonkusare2019naturalistic} for reviews).
% AV stimulus
The operationalization of visual perception is based on an annotation of cuts
and depicted locations in the audio-visual movie ``Forrest Gump'' (AV stimulus).
% AO stimulus
The operationalization of auditory perception is based on an annotation of
speech occurring in the movie's audio-description (AD stimulus).
% GLM contrasts
Based on these annotations, we created several general linear model (GLM)
contrast to analyze the corresponding publicly available fMRI datasets
(\href{http://www.studyforrest.org}{studyforrest.org}) of each naturalistic
stimulus \citep{hanke2016simultaneous, hanke2014audiomovie}.
% varying amount of data
Contrasts vary in HOW WELL / HOW MUCH DATA.\todo{intro too long already}

@@

% similar to previous studies
On the first level, we created GLM contrasts like studies that contrasted blocks
of pictures.
% dissimilar
But unlike previous studies, our approach was to contrast selected stimulus
features that we annotated in the audio-visual movie and its audio-description.
% intro
To test the robustness of this approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}) and eight $t$-contrasts for the AD stimulus (see Table
\ref{tab:ao-contrasts})
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in available data (i.e.
event counts).
% difference to Sengupta; Berman et al. (2010). Evaluating functional localizers
(2010) Notably, localization of the PPA in individual subjects that was done by
\citep{sengupta2016extension} using the established approach of contrasting
blocks of pictures is based on one contrast for each subjects (cf. Table 3 in
\citep{sengupta2016extension}) that was chosen post-hoc from a set of three
contrasts (\textit{strict}, \textit{relaxed}, and \textit{simple} contrast
\citep{sengupta2016extension}).\todo{maybe add note regarding Berman (2010); but
they did FFA}
% thus: primary contrasts
Here, we chose one contrast to be ``primary contrast'' for later detailed
inspection and report.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /

@@

@@

\todo[inline]{SE: overlap of clusters/contrasts: Anzahl der Überlappungen ist
schwer abzulesen; lieber eine andere Farbskala (spectral sequence?) nutzen; COH:
yes, I know it is kinda difficult, figures will be honed at the very end}

@@

% study goal
The goal of this study was to investigate if annotated cues about the spatial
layout embedded in two naturalistic stimuli correlate with increased hemodynamic
activity in the PPA that was defined using a visual localizer experiment within
the same subjects \citep{sengupta2016extension}.
% group level
On a group average level, we compare results gained from whole-brain GLM
analyses  of the movie and the audio-description (Z>3.4; p<.05, cluster
corrected) to results gained from the visual localizer.
% individual level
On the level single subjects (Z>3.4; p<.05, cluster corrected), we also assess
the performance of the exclusively auditory naturalistic stimulus as a
substitute for a visual paradigm to localize the PPA.\todo{``localize''}
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template can
found at \href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
\todo{private collection}

@@

\begin{table*}[h!]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting that was not depicted before to a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r. cuneal c., intracalcarine c., bilaterally occipital fusiform g., temporal fusiform c., posterior parahippocampal c.  \\
154 & 0.000000656 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 0.00000769 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

% table group results primary AD contrast
\begin{table*}[h!]
    \caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
        of the primary $t$-contrast for the audio-description comparing
        geometry-related nouns to non geometry-related nouns spoken by the
        audio-description's narrator (\texttt{geo, groom > all non-geo}).
        Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
followed by brain structures from posterior to anterior, and partially covered
areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
    \label{tab:res-ao-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
188 & 0.0000000596 & 4.48 & -17.5 & -65.5 & 25.5 & -14.7 & -59.1 & 15.2 & l. precuneus \\
164 & 0.000000238 & 4.47 & 17.5 & -58 & 23 & 15.6 & -55.6 & 16 & r. precuneus; \\
83 & 0.000128 & 4.48 & 27.5 & -43 & -17 & 27.2 & -41.1 & -14 & r. temporal (occipital) fusiform c.; posterior parahippocampal g. \\
73 & 0.000318 & 3.93 & -22.5 & -43 & -12 & -23.9 & -43.6 & -11.2 & l. lingual g.; temporal (occipital) fusiform g., posterior parahippocampal c. \\
63 & 0.000824 & 4.1 & 40 & -75.5 & 30.5 & 40.9 & -76.3 & 28.6 & r. superior lateral occipital c. \\
37 & 0.0129 & 4.24 & -37.5 & -78 & 33 & -38.4 & -79.5 & 28.9 & l. superior lateral occipital c. \\
\bottomrule
\end{tabular}
\end{table*}

@@

\todo[inline]{I tried to keep it concise but detailed; if individual contrasts
are mentioned (enumerated at the moment)}

% AV PPA contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r), VisC (l/r),
% intracalcarine, cuneal, ling.c
% 2 PPA (l/r); RSC (-/-), LOC (l/r), VisC (-/-)
% 3 PPA (l/r); RSC (-/-), LOC (-/-), VisC (-/r), occ. fusisf. g.
% 4 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), lingual g., occ. fusif. g.
% 5 PPA (l/r); RSC (l/r), LOC (l/r), VisC (-/-), occ. fusif. g.

@@

% AD PPA contrasts
% 1 PPA (l/r); RSC (l/r), LOC (l/r)
% 2 PPA (l/r); RSC (l/r), LOC (l/r), r. sup.temp.C., r.fr.pole; putamen; etc
% 3 PPA (l/r); RSC (l/r), LOC (l/r),l&r sup.temp.C., anterior cing., paracing.
% 4 PPA (l/r); RSC (l/r), LOC (l/r)
% 5 PPA (l/r); RSC (l/r), LOC (-/-)
% 6 PPA (l/r); RSC (l/r), LOC (l/-), l&r sup.temp.C.; medial pref. c., precun
% 7 PPA (-/-); RSC (l/r), LOC (l/-), l&r sup.temp.C
% 8 PPA (-/-); RSC (-/-), LOC (-/-)

% AD
Reliably across the five contrasts of the AV stimulus, we find bilaterally
significant clusters also in the ventral precuneal cortex / posterior cingulate
gyrus (i.e. restrosplenial region; contrasts 1, 4, 5) and lateral occipital
cortex (contrasts 1, 2, 4, 5)
% AD; LOC: AV cluster are more medial, AD clusters are more lateral
Reliably across the five contrasts of the AD stimulus, we find bilaterally
significant clusters in the ventral precuneus (all except contrasts 8), lateral
occipital cortex (bilateral in 4 contrasts 1 to 4, unilateral in contrasts 6 and
7), and superior temporal cortices (bilateral in contrasts 3, 6, 7; unilateral
right in contrast 2).
% non-systematic
Contrast 2 also shows bilateral clusters in the anterior cingulate gyrus and
right paracingulate gyrus (frontal medial cortex), right putamen, and right
frontal pole.
%
Contrast 3 shows clusters bilaterally in the anterior cingulate gyrus and
left frontal pole.
%
Contrast 6 shows one additional cluster also in the right medial frontal cortex.

@@

% ---------- AV control contrasts ----------
% 6 nothing
% 7 nothing
% 8 nothing
% 9 nothing
%10 se_new > se_old (nouns but in AV stimulus):
% LOC (l/r) right PPA, bilateral sup. lat. occ. c., sup. parietal lobe (right)

% ---------- AD control contrasts ----------
% 9 PPA (-/-); RSC (-/r), LOC (-/-), left pars triangularis
%10 PPA (-/-); RSC (-/-), LOC (-/-)
%11 PPA (-/-); RSC (-/-), LOC (-/-),
%12 PPA (-/-); RSC (-/-), LOC (-/-), right posterior hippocampus
%13 PPA (-/-); RSC (-/-), LOC (-/-)

% intro
Lastly, we implemented five contrasts for every stimulus for the purpose of
negative control.
% AV: no_cut > x
In the analysis of the AV data, none of the contrasts that compared the ``no cut
condition''  to a movie cut category (contrasts 6, 7, 8, 9) yielded significant
clusters.
% AV using nouns
The contrast that used the narrator's nouns but in the AV stimulus (se\_new >
se\_old) yielded a significant cluster in the right PPA and bilateral clusters
in the superior lateral occipital cortices (the right hemispheric cluster
extending into the superior parietal cortex).

% AD stimulus
In the analysis of the AD data, we created control contrasts based on events of
the annotated movie cuts (cf. Table \ref{tab:ao-contrasts})
% contrast 9
Contrast 9 (vse\_new > pe\_old) revealed one significant cluster in the left
inferior prefrontal cortex (pars triangularis) and right ventral
precuneus/posterior cingulate gyrus.
% contrast 12
Contrast 12 (\texttt{vse\_new} > \texttt{vse\_old}, \texttt{vpe\_old}) revealed
one cluster in the right posterior hippocampus. \todo{dorsally of PPA}

\todo[inline]{there is no table/figure for negative control contrasts; we could
add a reference to NeuroVault (here again) or point to the dataset}

@@

@@

% AV: contrast with AV nouns
Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new
setting are correlated  with cuts to a new setting (vse\_new; r$\approx$0.3;
second highest correlation of a verbal cue category with a cut category; AND:
nouns that cue change to a familiar setting are somewhat correlated with cuts to
a familiar setting (se\_old; r$\approx$0.4; highest correlation of a verbal
category with a cut category).

% AD: correlation of these nouns with cuts
Compare Figure \ref{fig:reg-corr}: nouns that cue change to a new setting are
correlated  with cuts to a new setting (vse\_new; r$\approx$0.3; second highest
correlation of a verbal cue category with a cut category.
